Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model

### 2021-06-29 SIR_manuscript.tex
discussion covered

\david{The intro and discussion would benefit from (potentially many) additional references.}
Although testing and tracing is a key part of infection control strategies, mathematical epidemiologists have typically analyzed it with detailed models designed to inform particular public health efforts \ali{\citep{endo2020implication,hellewell2020feasibility,jenness2020modeling}}, rather than analyzing simple but general models of the feedback between testing and transmission dynamics.
\ali{the following sentences added to address Ben's comment:} There have been several modeling studies of testing and tracing dynamics and their interaction with epidemiological dynamics. In the context of repeated screening and random testing of isolated populations (such as a university), \cite{bergstrom2020frequency} provided some analytical results\david{what are the results?  that's what is most important, not whether the results were analytical}, \cite{rogers2021high} simulated a SEIR model with high-low \david{meaning?} testing intensity and sensitivity\david{what did they find?}. Further, \cite{friston2021testing} model the effects of self-isolation on testing and tracing\david{what did they find?}. Our modeling approach is novel compared to these works\david{how so?  You can't just say our work is novel.  What makes it novel relative to these previous papers?}. We hope that the present paper will inspire further explorations of the fundamental properties of epidemic models that incorporate explicit testing processes.

>>>>

\david{The intro and discussion would benefit from (potentially many) additional references.}
Although testing and tracing is a key part of infection control strategies, mathematical epidemiologists have typically analyzed it with detailed models designed to inform particular public health efforts \ali{\citep{endo2020implication,hellewell2020feasibility,jenness2020modeling}}, rather than analyzing simple but general models of the feedback between testing and transmission dynamics.
\ali{the following sentences added to address Ben's comment:} There have been several modeling studies of testing and tracing dynamics and their interaction with epidemiological dynamics. In the context of repeated screening and random testing of isolated populations (such as a university), \cite{bergstrom2020frequency} provided some analytical results which suggests, as an outbreak control strategy, that proactively screening asymptomatic individuals and isolating confirmed-positive cases would reduce the spread of the disease. In particular, They explored the effects of testing frequency and Trade-offs between frequency, accuracy and the reporting delay on the epidemic dynamic (more specifically, on the effective reproductive number).
\cite{rogers2021high} simulated a SEIR model with testing and isolation which suggest a combination of rapid testing with antigen tests and the subsequent isolation of confirmed-positive individuals
a strategy for controlling the disease dynamics in the \covid pandemic. Further, \cite{friston2021testing} model the effects of self-isolation on testing and tracing with the focused on posterior predictions and projections under different testing and tracing scenarios. They conclude that the emergence of a second wave depends almost exclusively on the rate at which immunity is lost and that it is necessary to track the 20\% of asymptomatic individuals in order to control the outbreak. Our modeling approach is novel compared to these works as it mechanistically incorporates the epidemic and testing processes with different levels of testing focus from random to highly targeted. We hope that the present paper will inspire further explorations of the fundamental properties of epidemic models that incorporate explicit testing processes.
